Combining genomic prediction with citizen science for crop improvement and early selection in durum wheat

### 2019-06-17 manuscript/manuscript.Rmd
data

Kauê de Sousa^1,2^, Jacob van Etten^2^, Carlo Fadda^3^, Yosef Gebrehawaryat^3^, Jean-Luc Jannink^4,5^, Basazen Fantahun Lakew^6^, Dejene Mengistu^7^, Svein Ø. Solberg^1^, Mario Enrico Pè^6^, Jesse Poland^8^, [… add others], Melfa and Workaye Farmer Community, Matteo Dell’Acqua^6[*]^  
^1^ Department of Agricultural Sciences, Inland Norway University of Applied Sciences, 2318 Hamar, Norway ^2^ Bioversity International, Costa Rica Office, 30501 Turrialba, Costa Rica   
^3^ Bioversity International, Ethiopia Office, 1000 Addis Ababa, Ethiopia  
^4^ College of Agriculture and Life Sciences, Cornell University, 14853 Ithaca, USA  
^5^ Agricultural Research Service, United States Department of Agriculture, 148532901, Ithaca, USA  
^6^ Scuola Superiore Sant’Anna, Institute of Life Sciences, 56124 Pisa, Italy  
^7^ Bioversity International, Nepal Office, 3055 Kathmandu, Nepal 
^8^ Kansas State University, Kansas, USA
^[*]^To whom correspondence must be addressed <m.dellacqua@santannapisa.it>

@@

* Is genomic selection with citizen science a viable approach?
* Does the genetic information provide sufficient gain in the predictions for variety selection (given the cost)?
* Can the combination of genomic and citizen science provide new insights in which traits farmers prioritise or which areas of the genome play a role?
* Does genomic prediction using phenotypic data produced on station (agronomic traits, farmer preferences) improve accuracy in the field as measured in the tricot trial?

@@

* Crowdsourcing citizen science showed the ability to register the climate effects as they occurr in farms, with potential to be used in plant breeding programs and risk assessments for farm adaptation[@VanEtten2019].

>>>>

Kauê de Sousa^1,2^, Jacob van Etten^2^, Carlo Fadda^3^, Yosef Gebrehawaryat^3^, Jean-Luc Jannink^4,5^, Basazen Fantahun Lakew^6^, Dejene Mengistu^7^, Svein Ø. Solberg^1^, Mario Enrico Pè^6^, Jesse Poland^8^, [… add others], Melfa and Workaye Farmer Community, Matteo Dell’Acqua^6[*]^  
^1^ Department of Agricultural Sciences, Inland Norway University of Applied Sciences, 2318 Hamar, Norway  
^2^ Bioversity International, Costa Rica Office, 30501 Turrialba, Costa Rica   
^3^ Bioversity International, Ethiopia Office, 1000 Addis Ababa, Ethiopia  
^4^ College of Agriculture and Life Sciences, Cornell University, 14853 Ithaca, USA  
^5^ Agricultural Research Service, United States Department of Agriculture, 148532901, Ithaca, USA  
^6^ Scuola Superiore Sant’Anna, Institute of Life Sciences, 56124 Pisa, Italy  
^7^ Bioversity International, Nepal Office, 3055 Kathmandu, Nepal  
^8^ Kansas State University, Kansas, USA  
^[*]^Correspondence should be addressed to MDA (email: <m.dellacqua@santannapisa.it>)

@@

* Can farmers' evaluations better predict varietal performance associated with genes?
* Can we use crowdsourcing to improve GxE estimates?
* What is the ability of local varieties to outperform varieties from other zones?

@@

* Crowdsourcing citizen science showed the ability to register the climate effects as they occur in farms, with potential to be used in plant breeding programs and risk assessments for farm adaptation[@VanEtten2019].
